The 2014 SMT Competition

### 2015-08-03 2014/report/SMTCOMP.tex
Minor.

SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal
of the competition. The new computational infrastructure, StarExec, worked very well for the purpose. The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed. Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years. As a partial comparison, solvers that performed well in previous years are included in the this year's competition. However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.

@@

\begin{itemize}
\item The organizers were supported by their respective institutions (GrammaTech, Federal University of Rio Grande do Norte, Brazil and Uppsala University, Sweden respectively).

\item In addition Cok received partial support from the U.S.\ National Science Foundation
under grant ACI-1314674.

@@

\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running;
in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.
%
The StarExec cluster is supported by
U.S.\ National Science Foundation under grants \#1058748 and \#1058925.
%
\item The cost of executing the SMT Competition is underwritten by the SMT Workshop.
\end{itemize}

Any opinions,
findings, and conclusions or recommendations expressed in this
material are those of the authors and do not necessarily reflect the
views of the National Science Foundation.

@@

\thebibliography

>>>>

SMT-COMP 2014 successfully executed the comparison among solvers that is the main goal of the competition. The new computational infrastructure, StarExec, worked very well for the purpose. The competition saw a renewed interest in participation\textemdash there were record numbers of teams participating, solvers entered, teams and solvers that had never before participated, benchmarks used, and amount of computation performed. Although the 2014 results are not readily comparable to previous years (because of changes in benchmarks and equipment), the detailed performance of each solver on each benchmark from this first year using StarExec will be a solid baseline to measure improvements in the state-of-the-art of solver performance in future years. As a partial comparison, solvers that performed well in previous years were included in this year's competition. However, rerunning the competition on the old hardware or on the old benchmarks was out of the scope of the organizers' task.

@@

\begin{itemize}
\item The organizers were supported by their respective institutions (GrammaTech, Federal University of Rio Grande do Norte, Brazil and Uppsala University, Sweden respectively).  In addition, Cok received partial support from the U.S.\ National Science Foundation under grant ACI-1314674.

@@

\item Aaron Stump and the StarExec support team were essential in keeping the competition cluster running; in this first large-scale, public use of the cluster, numerous small details needed correction and were corrected promptly.  The StarExec cluster is supported by the U.S.\ National Science Foundation under grants \#1058748 and \#1058925.

\item The cost of executing the SMT Competition is underwritten by the SMT Workshop.
\end{itemize}

Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors, and do not necessarily reflect the views of the National Science Foundation.

@@
